SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-11-25 toplas26/model.tex
checkpoint

\begin{definition}
  Given $\pmf$, the \emph{conditional distribution}
  of $X_1$ given $X_2$ where $X_1 \cup X_2 = \dom(\pmf)$ 
  is denoted $\condd{\pmf}{X_1}{X_2}$ and defined as follows:
  $$
  \forall \store \in \mems(X_1 \cup X_2)\ .\ 
  \condd{\pmf}{X_1}{X_2}(\store) \defeq
  \begin{cases}
    \begin{array}{ll}
      0 & \text{\ if\ } \margd{\pmf}{X_2}(\store_{X_2}) = 0\\
      \pmf(\store) / \margd{\pmf}{X_2}(\store_{X_2})\ & \text{\ o.w.}
     \end{array}
  \end{cases}
  $$
\end{definition}
We also define some convenient syntactic sugaring for ``implicit
marginalization'' given a realization.
%The first will allow us to
%compare marginal distributions under different realization conditions
%(as in, e.g., Definition \ref{definition-NIMO}), the others are standard.
\begin{definition}
  Given $\pmf$ and $X \subseteq \dom(\pmf)$, for all $\store \in \mems(X)$
  define $\pmf(\store)  \defeq \margd{\pmf}{X}(\store)$.
  %and
  %$\store_2 \in \mems(X_2)$ define
  %$\pmf(\store_1)  \defeq \margd{\pmf}{X_1}(\store_1)$ 
  %\begin{enumerate}
  %\item $\condd{\pmf}{X_1}{\store_2}(\store_1) \defeq \condd{\pmf}{X_1}{X_2}(\store_1 \uplus \store_2)$
  %\item $\pmf(\store_1)  \defeq \margd{\pmf}{X_1}(\store_1)$ 
  %\item $\pmf(\store_1|\store_2) \defeq \condd{\pmf}{X_1}{X_2}(\store_1 \uplus \store_2)$
  %\end{enumerate}
\end{definition}
As in previous work \cite{darais2019language,barthe2019probabilistic,skalka-near-ppdp24,li2023lilac}, 
probabilistic independence, aka separation, is an important concept and we adopt the
following standard notation to express conditional and unconditional separation:
\begin{definition}
%  We write $\vc{\pmf}{x}{y}$ iff $\pmf(\{ x \mapsto 0\}\ |\ \{ y \mapsto 0 \}) =
%  \pmf(\{ x \mapsto 1\}\ |\ \{ y \mapsto 1 \}) = 1$.
  We write $\condsep{\pmf}{X_1}{X_2}{X_3}$ iff for all
    $\store \in \mems(X_1 \cup X_2)$ and $\store' \in \mems(X_3)$ we have
  $\pmf(\store|\store') =
  \pmf(\store_{X_1}|\store') * \pmf(\store_{X_2}|\store')$. If $X_1$ is empty
  we write $\sep{\pmf}{X_2}{X_3}$.
\end{definition}

@@

Information about honest secrets can be revealed to corrupt clients
through messages sent from honest to corrupt clients, and through
publicly broadcast information from honest clients. Dually,
corrupt clients can impact protocol integrity through the messages
sent from corrupt to honest clients, and through publicly broadcast information
from corrupt clients. We call the former \emph{corrupt views}, and
the latter \emph{honest views}. We let $V$ range over sets
of views, i.e., subsets of $M \cup P$.
\begin{definition}[Corrupt and Honest Views]
  We let $V$ range over \emph{views} which are sets of messages
  and reveals. Given a program $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$,
  define $\views(\prog) \defeq M \cup P$. Letting $I_1$, $I_2$ be
  a partitioning of the federation clients, define:
  \begin{array}{lcl}
    V_{I_1 \rhd I_2} & \defeq
        & \{\ \rvl{w} \mid\ \reveal{w}{\be}{\cid} \in \prog \wedge \cid \in I_1 \ \}\ \cup\ %\\
    % & &
    \{\ \elab{\mesg{w}}{\cid}\ \mid\  \eassign{\mesg{w}}{\cid}{\be}{\cid'} \in
           \prog \wedge \cid \in I_2 \wedge \cid' \in I_1 \ \} 
  \end{array}
  $$
  Given a partitioning of the federation $H,C$, we call $\houtputs$
  \emph{corrupt views} and $\hinputs$ \emph{honest views}.
\end{definition}

@@

Since MPC protocols release some information about secrets through
outputs of $\idealf$, they do not enjoy strict noninterference.
Public reveals and protocol outputs are fundamentally forms of
declassification. But the following property of probabilistic
noninterference \emph{conditioned on output} is sound for passive
security \cite{skalka-near-ppdp24}.
\begin{definition}[Noninterference modulo output]
  \label{definition-NIMO}
  We say that a program $\prog$ with $\iov(\prog) = S \cup V \cup O$
  satisfies \emph{noninterference modulo output}
  iff for all $H$ and $C$ %and $\store_1 \in \mems(S_C \cup O)$ and $\store_2 \in \mems(\houtputs)$
  we have:
  $$
  \condd{\progtt(\prog)}{S_H}{S_C \cup O} = \condd{\progtt(\prog)}{S_H}{S_C \cup O \cup \houtputs}
 $$
\end{definition}
This conditional noninterference property implies that
corrupt views give the adversary no better chance of guessing honest
secrets than just the output and corrupt inputs do.

@@

\emph{Integrity} is an important hyperproperty in security models that
admit malicious adversaries. Consistent with formulations in
deterministic settings, we define protocol integrity as the
preservation of high equivalence (of secrets and views). Intuitively,
this property says that any adversarial strategy either ``mimics'' a
passive strategy with some choice of inputs or causes an abort.
\begin{definition}[Integrity]
  \label{def-integrity}
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$, $C$, and $\adversary$,
  if $\store \in \aruns(\prog)$ we have:
    $$
    \condd{\progtt(\prog,\adversary)}{X}{S_H \cup \cinputs} =
    \condd{\progtt(\prog)}{X}{S_H \cup \cinputs}
    $$ 
  where $X \defeq (\houtputs \cup O_H) \cap \dom(\store)$. 
\end{definition}
Integrity plus noninterference modulo output implies malicious security
in the real/ideal model \cite{skalka-near-ppdp24}, and integrity plus
gradual release is a probabilistic form of robust declassification
\cite{sabelfeld2009declassification}.

>>>>

\begin{definition}
  Given $\pmf$, the \emph{conditional distribution}
  of $X_1$ given $X_2$ where $X_1 \cup X_2 = \dom(\pmf)$ 
  is denoted $\condd{\pmf}{X_1}{X_2}$ and defined as follows:
  $$
  \forall \store \in \mems(X_1 \cup X_2)\ .\ 
  \condd{\pmf}{X_1}{X_2}(\store) \defeq
  \begin{cases}
    \begin{array}{ll}
      0 & \text{\ if\ } \margd{\pmf}{X_2}(\store_{X_2}) = 0\\
      \pmf(\store) / \margd{\pmf}{X_2}(\store_{X_2})\ & \text{\ o.w.}
     \end{array}
  \end{cases}
  $$
\end{definition}
We also define some convenient syntactic sugaring for application of
pmfs to realizations when their domains don't match.
%The first will allow us to
%compare marginal distributions under different realization conditions
%(as in, e.g., Definition \ref{definition-NIMO}), the others are standard.
\begin{definition}
  Given $\pmf$ and $\store$ with $\dom(\pmf) \ne \dom(\store)$,
  $\pmf(\store) \defeq \margd{\pmf}{\dom(\store) \cap \dom(\pmf)}(\store_{\dom(\store) \cap \dom(\pmf)})$.
  %\defeq \margd{\pmf}{\dom(\store)}(\store)$
  %if $\dom(\store) \subset \dom(\pmf)$, and define $\pmf(\store) \defeq \pmf(\store_{\dom(\pmf)})$ if
  %$\dom(\pmf) \subset \dom(\store)$.
  %and
  %$\store_2 \in \mems(X_2)$ define
  %$\pmf(\store_1)  \defeq \margd{\pmf}{X_1}(\store_1)$ 
  %\begin{enumerate}
  %\item $\condd{\pmf}{X_1}{\store_2}(\store_1) \defeq \condd{\pmf}{X_1}{X_2}(\store_1 \uplus \store_2)$
  %\item $\pmf(\store_1)  \defeq \margd{\pmf}{X_1}(\store_1)$ 
  %\item $\pmf(\store_1|\store_2) \defeq \condd{\pmf}{X_1}{X_2}(\store_1 \uplus \store_2)$
  %\end{enumerate}
\end{definition}
As in previous work \cite{darais2019language,barthe2019probabilistic,skalka-near-ppdp24,li2023lilac}, 
probabilistic independence, aka separation, is an important concept and we adopt the
following standard notation to express conditional and unconditional separation:
\begin{definition}
  \label{def-condsep}
%  We write $\vc{\pmf}{x}{y}$ iff $\pmf(\{ x \mapsto 0\}\ |\ \{ y \mapsto 0 \}) =
%  \pmf(\{ x \mapsto 1\}\ |\ \{ y \mapsto 1 \}) = 1$.
  We write $\condsep{\pmf}{X_1}{X_2}{X_3}$ iff $\condd{\pmf}{X_2 \cup X_3}{X_1}
  = \condd{\pmf}{X_2}{X_1} * \condd{\pmf}{X_3}{X_1}$. If $X_1$ is empty
  we write $\sep{\pmf}{X_2}{X_3}$.
\end{definition}

@@

Information about honest secrets can be revealed to corrupt clients
through messages sent from honest to corrupt clients, and through
publicly broadcast information from honest clients. Dually,
corrupt clients can impact protocol integrity through the messages
sent from corrupt to honest clients, and through publicly broadcast information
from corrupt clients. We call the former \emph{corrupt views}, and
the latter \emph{honest views}. We let $V$ range over sets
of views, i.e., subsets of $M \cup P$.
\begin{definition}[Corrupt and Honest Views]
  We let $V$ range over \emph{views} which are sets of messages
  and reveals. Given a program $\prog$ with $\iov(\prog) = S \cup M \cup P \cup O$,
  define $\views(\prog) \defeq M \cup P$. Letting $I_1$, $I_2$ be
  a partitioning of the federation clients, define:
  $$
  \begin{array}{lcl}
    V_{I_1 \rhd I_2} & \defeq
        & \{\ \rvl{w} \mid\ \reveal{w}{\be}{\cid} \in \prog \wedge \cid \in I_1 \ \}\ \cup\ %\\
    % & &
    \{\ \elab{\mesg{w}}{\cid}\ \mid\  \eassign{\mesg{w}}{\cid}{\be}{\cid'} \in
           \prog \wedge \cid \in I_2 \wedge \cid' \in I_1 \ \} 
  \end{array}
  $$
  Given a partitioning of the federation $H,C$, we call $\houtputs$
  \emph{corrupt views} and $\cinputs$ \emph{honest views}.
\end{definition}

@@

Since MPC protocols release some information about secrets through
outputs of $\idealf$, they do not enjoy strict noninterference.
Public reveals and protocol outputs are fundamentally forms of
declassification. But the following property of probabilistic
noninterference \emph{conditioned on output} is sound for passive
security \cite{skalka-near-ppdp24}.
\begin{definition}[Noninterference modulo output]
  \label{definition-NIMO}
  We say that a program $\prog$ with $\iov(\prog) = S \cup V \cup O$
  satisfies \emph{noninterference modulo output}
  iff for all $H$ and $C$ and $\store \in \runs(\prog)$ 
  we have:
  $$
  \condd{\progtt(\prog)}{S_H}{S_C \cup O}(\store) = \condd{\progtt(\prog)}{S_H}{S_C \cup O \cup \houtputs}(\store)
 $$
\end{definition}
This conditional noninterference property implies that
corrupt views give the adversary no better chance of guessing honest
secrets than just the output and corrupt inputs do.

@@

\emph{Integrity} is an important hyperproperty in security models that
admit malicious adversaries. Consistent with formulations in
deterministic settings, we define protocol integrity as the
preservation of high equivalence (of secrets and views). Intuitively,
this property says that any adversarial strategy either ``mimics'' a
passive strategy with some choice of inputs or causes an abort.
\begin{definition}[Integrity]
  \label{def-integrity}
  We say that a protocol $\prog$ with $\iov(\prog) = S \cup V \cup O$ has
  \emph{integrity} iff for all $H$, $C$, and $\adversary$,
  if $\store \in \aruns(\prog)$ there exists $\store' \in \runs(\prog)$ with
  $\store_{S_H \cup X}' = \store_{S_H \cup X}$ and:
    $$
    \condd{\progtt(\prog,\adversary)}{X}{S_H \cup Y}(\store) =
    \condd{\progtt(\prog)}{X}{S_H \cup Y}(\store')
    $$ 
  where $X \defeq (\houtputs \cup O_H) \cap \dom(\store)$ and $Y = \cinputs \cap \dom(\store)$. 
\end{definition}
Integrity plus noninterference modulo output implies malicious security
in the real/ideal model \cite{skalka-near-ppdp24}, and integrity plus
gradual release is a probabilistic form of robust declassification
\cite{sabelfeld2009declassification}.

### 2025-11-25 toplas26/sty.tex
checkpoint

Now we define what we mean by soundness of $\genshares$. In essence
we mean perfect secrecy \cite{barthe2019probabilistic} in the context
of protocols where multiple encodings can occur. These
conditions are obviously met by, e.g., ``vanilla'' additive or Shamir
shares which generate shares in uniform marginal distributions.
\begin{definition}
  \label{def-genshares}
  We say that $\genshares$ is \emph{sound} iff given any $\prog$ with
  $\vars(\prog) = S \cup V \cup O \cup R$
  and $\phi$ and $\rx{w}{\cid} \not \in R$ and $\genshares(\phi,\rx{w}{\cid}) =
  \phi_1,\phi_2$ we have for all $a \in \setit{1,2}$:
  $$
  \sep{\progd(\prog)}{(S \cup V \cup O \cup \setit{\phi})}{\setit{\phi_a}}
  $$
\end{definition}

@@

    \Phi_a & \defeq & \setit{ \phi_a \mid ([\phi_1,\phi_2] : \sharety) \in \Gamma} \cup
                        \setit{ \phi_b \mid (\pubx{\recon(\phi_1,\phi_2)} : \sty) \in \Gamma} \\% \Phi_a^m \cup \Phi_a^p \\

@@

    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup \Phi^o}
    = 
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup  \Phi_a \cup \Phi^o}

@@

@@

    %$\condsep{\progd(\prog)}{\setit{\recon(\phi_i^1,\phi_i^2)}}{\setit{\phi_i^b}}{\recon(\phi_i^1,\phi_i^2)}$
    $$\condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup  \Phi_a \cup \Phi^o \cup \setit{\recon(\phi_i^1,\phi_i^2)}} =
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}}  \cup  \Phi_a \cup \Phi^o \cup \setit{\recon(\phi_i^1,\phi_i^2), \phi_i^b}}$$

@@

Next we show that, given well-formed typing environments, share type judgements preserve
the important properties (i-ii) in Definitions \ref{def-OK}. This result follows from
known semi-homomorphic properties of non-interactive operations that are syntactically
verified in typing judgements.
\begin{lemma}
  \label{lemma-sty-noninteractive-sound}
  Given $\prog,\Gamma,R : {OK}$ where $\secrets(\prog) = S$. For all $a,b\in \setit{1,2}$ with $a \ne b$ let:
  \begin{eqnarray*}
    %\Phi_a^m & \defeq & \setit{ \phi_a \mid ([\phi_1,\phi_2] : \sharety) \in \Gamma} \\
    %\Phi_a^p & \defeq & \setit{ \phi_b \mid (\pubx{\recon(\phi_1,\phi_2)} : \sty) \in \Gamma}\\
    \Phi_a & \defeq & \setit{ \phi_a \mid ([\phi_1,\phi_2] : \sharety) \in \Gamma} \cup
                        \setit{ \phi_b \mid (\pubx{\recon(\phi_1,\phi_2)} : \sty) \in \Gamma} \\% \Phi_a^m \cup \Phi_a^p \\
    \Phi^o & \defeq & \setit{ \recon(\phi_1,\phi_2) \mid (\pubx{\recon(\phi_1,\phi_2)} : \outty) \in \Gamma}
  \end{eqnarray*} 
  and also suppose $\Gamma, \toeq{\prog} \vdash [\phi_1,\phi_2] : \sharety$.
  Then for all $a,b \in \setit{1,2}$ with $a \ne b$ the following conditions hold:
    \begin{enumerate}[\hspace{5mm}i.]
    \item
    $
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup \Phi^o}
    = 
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup  \Phi_a \cup \setit{\phi_a} \cup \Phi^o}
    $
  \item 
    $\condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}} \cup  \Phi_a \cup \Phi^o \cup \setit{\recon(\phi_1,\phi_2)}} =
    \condd{\progtt(\prog)}{S_{\setit{\cid_a}}}{S_{\setit{\cid_b}}  \cup  \Phi_a \cup \Phi^o \cup \setit{\recon(\phi_1,\phi_2), \phi_b}}$
    \end{enumerate}
\end{lemma}
\begin{proof}
  The proof is by induction on the derivation of $\Gamma, \toeq{\prog} \vdash [\phi^1,\phi^2] : \sharety$.
  In the base case where the judgement follows by the \TirName{Shared} rule, the result
  follows trivially by Definition \ref{def-OK}. In cases \TirName{HEAdd}, \TirName{HEAddPub}, and
  \TirName{HEMultPub} the result follows by Definition \ref{def-OK} and known
  semi-homomorphic properties of secret sharing \cite{10.1007/978-3-030-68869-1_3}.
  Case \TirName{ShareEntails} follows by correctness of the SMT interpretation of
  protocols as in Theorem \ref{theorem-toeq}.
\end{proof}

@@

In addition to typing judgements, in order to show that a protocol is
secure, we need to classify all corrupt views as shares, all
public values as secure openings, and all outputs as reconstructed
shares by adding them to $\Gamma$. We capture this formally with the following notion of
type environment closure.
\begin{definition}
  \label{def-sty-closed}
  $\Gamma$ is \emph{closed for $\prog$} iff for all $H,C$,
  for all $x \in \houtputs$ there exists $\phi$ such that either
  $([x,\phi] : \sharety) \in \Gamma$ if $C = \setit{1}$
  or  $([\phi,x] : \sharety) \in \Gamma$ if $C = \setit{2}$,
  and for all $\out{\cid} \in O$ we have $(\pubx{\out{\cid}} : \outty) \in \Gamma$.
\end{definition}
Now, the following is a consequence of Definitions \ref{def-OK} and \ref{def-sty-closed}, and then
our main Theorem \ref{theorem-sty} follows by Lemma \ref{lemma-OK} and Theorem \ref{theorem-OK}.
\begin{theorem}
  \label{theorem-OK}
  If $\prog,\Gamma,R : {OK}$ and $\Gamma$ is closed
  for $\prog$, then $\prog$ satisfies noninterference modulo output. 
\end{theorem}
\begin{proof}
  Let $\iov(\prog) = S \cup V \cup O$ and assume some partitioning $H,C$
  with $H = \setit{b}$ and $C = \setit{a}$ for $a,b \in \setit{1,2}$.
  %For any $\out{\cid} \in O$ with $\Gamma,\toeq{\prog} \vdash \pubx{\out{\cid}} : \outty$
  %we can assume wlog that $(\out{\cid} : \outty) \in \Gamma$, since we can
  %add the binding to $\Gamma'$ with  $\prog,\Gamma',R  : {OK}$ by Lemma
  %\ref{lemma-OK}.
  Let $\Phi_a$ and $\Phi^o$ be as defined in Definition \ref{def-OK}. 
  By Definition \ref{def-sty-closed} we have that $x \in \houtputs$
  implies $x \in \Phi_a$ and $(\out{\cid} : \outty) \in \Gamma$ for all
  $\out{\cid} \in O$. 
  Therefore by Definition \ref{def-OK} (and marginalizing away
  extraneous $(\stt : \sty) \in \Gamma$) we have:
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O} = \condd{\progd(\prog)}{S_H}{S_C \cup \houtputs \cup \Phi^o \cup O}
  $$
  By definition of $\TirName{Output}$ it is also the case that for all
  $\out{\cid} \in O$ we have $\toeq{\prog} \models o = \phi$ for some
  $\phi \in \Phi^o$. Therefore we have:
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O} = \condd{\progd(\prog)}{S_H}{S_C \cup \houtputs \cup O}
  $$
  which is noninterference modulo output by Definition \ref{definition-NIMO}.
\end{proof}

>>>>

Now we define what we mean by soundness of $\genshares$. In essence
we mean perfect secrecy \cite{barthe2019probabilistic} in the context
of protocols where multiple encodings can occur. These
conditions are obviously met by, e.g., ``vanilla'' additive or Shamir
shares which generate shares in uniform marginal distributions. Here
and later we leverage (conditional) probabilistic independence as
characterized in Definition
\ref{def-condsep}.
\begin{definition}
  \label{def-genshares}
  We say that $\genshares$ is \emph{sound} iff given any $\prog$ with
  $\vars(\prog) = S \cup V \cup O \cup R$
  and $\phi$ and $\rx{w}{\cid} \not \in R$ and $\genshares(\phi,\rx{w}{\cid}) =
  \phi_1,\phi_2$ we have for all $a \in \setit{1,2}$:
  $$
  \sep{\progd(\prog)}{(S \cup V \cup O \cup \setit{\phi})}{\setit{\phi_a}}
  $$
\end{definition}

@@

    \Phi_b & \defeq & \setit{ \phi_b \mid ([\phi_1,\phi_2] : \sharety) \in \Gamma} \cup
                        \setit{ \phi_a \mid (\pubx{\recon(\phi_1,\phi_2)} : \sty) \in \Gamma} \\% \Phi_a^m \cup \Phi_a^p \\

@@

    \condsep{\progtt(\prog)}{(S_{\setit{b}} \cup \Phi^o)}{\Phi_b}{S_{\setit{a}}}

@@

    %$
    %\condd{\progtt(\prog)}{S_{\setit{a}}}{S_{\setit{b}} \cup \Phi^o}
    %= 
    %\condd{\progtt(\prog)}{S_{\setit{a}}}{S_{\setit{b}} \cup  \Phi_a \cup \Phi^o}
    %$.

@@

    $$\condsep{\progd(\prog)}{(S_{\setit{b}} \cup  \Phi_b \cup \Phi^o \cup \setit{\recon(\phi_i^1,\phi_i^2)})}{\phi_i^a}{S_{\setit{a}}}$$
    %$$\condd{\progtt(\prog)}{S_{\setit{a}}}{S_{\setit{b}} \cup  \Phi_a \cup \Phi^o \cup \setit{\recon(\phi_i^1,\phi_i^2)}} =
    %\condd{\progtt(\prog)}{S_{\setit{a}}}{S_{\setit{b}}  \cup  \Phi_a \cup \Phi^o \cup \setit{\recon(\phi_i^1,\phi_i^2), \phi_i^b}}$$

@@

Next we show that, given well-formed typing environments, share type judgements preserve
the important properties (i-ii) in Definitions \ref{def-OK}. This result follows from
known semi-homomorphic properties of non-interactive operations that are syntactically
verified in typing judgements.
\begin{lemma}
  \label{lemma-sty-noninteractive-sound}
  Given $\prog,\Gamma,R : {OK}$ where $\secrets(\prog) = S$. For all $a,b\in \setit{1,2}$ with $a \ne b$ let:
  \begin{eqnarray*}
    %\Phi_a^m & \defeq & \setit{ \phi_a \mid ([\phi_1,\phi_2] : \sharety) \in \Gamma} \\
    %\Phi_a^p & \defeq & \setit{ \phi_b \mid (\pubx{\recon(\phi_1,\phi_2)} : \sty) \in \Gamma}\\
    \Phi_b & \defeq & \setit{ \phi_b \mid ([\phi_1,\phi_2] : \sharety) \in \Gamma} \cup
                        \setit{ \phi_a \mid (\pubx{\recon(\phi_1,\phi_2)} : \sty) \in \Gamma} \\% \Phi_a^m \cup \Phi_a^p \\
    \Phi^o & \defeq & \setit{ \recon(\phi_1,\phi_2) \mid (\pubx{\recon(\phi_1,\phi_2)} : \outty) \in \Gamma}
  \end{eqnarray*} 
  and also suppose $\Gamma, \toeq{\prog} \vdash [\phi_1,\phi_2] : \sharety$.
  Then for all $a,b \in \setit{1,2}$ with $a \ne b$ the following conditions hold:
    \begin{enumerate}[\hspace{5mm}i.]
    \item
      $
      \condsep{\progtt(\prog)}{(S_{\setit{b}} \cup \Phi^o)}{(\Phi_b \cup \setit{\phi_b})}{S_{\setit{a}}}
      $
    %$
    %\condd{\progtt(\prog)}{S_{\setit{a}}}{S_{\setit{b}} \cup \Phi^o}
    %= 
    %\condd{\progtt(\prog)}{S_{\setit{a}}}{S_{\setit{b}} \cup  \Phi_a \cup \setit{\phi_a} \cup \Phi^o}
    %$
    \item
       $\condsep{\progtt(\prog)}{(S_{\setit{b}} \cup  \Phi_b \cup \Phi^o \cup \setit{\recon(\phi_1,\phi_2)})}{\phi_a}{S_{\setit{a}}}$
    %$\condd{\progtt(\prog)}{S_{\setit{a}}}{S_{\setit{b}} \cup  \Phi_a \cup \Phi^o \cup \setit{\recon(\phi_1,\phi_2)}} =
    %\condd{\progtt(\prog)}{S_{\setit{a}}}{S_{\setit{b}}  \cup  \Phi_a \cup \Phi^o \cup \setit{\recon(\phi_1,\phi_2), \phi_b}}$
    \end{enumerate}
\end{lemma}
\begin{proof}
  The proof is by induction on the derivation of $\Gamma, \toeq{\prog} \vdash [\phi^1,\phi^2] : \sharety$.
  In the base case where the judgement follows by the \TirName{Shared} rule, the result
  follows trivially by Definition \ref{def-OK}. In cases \TirName{HEAdd}, \TirName{HEAddPub}, and
  \TirName{HEMultPub} the result follows by Definition \ref{def-OK} and known
  semi-homomorphic properties of secret sharing \cite{10.1007/978-3-030-68869-1_3}.
  Case \TirName{ShareEntails} follows by correctness of the SMT interpretation of
  protocols as in Theorem \ref{theorem-toeq}.
\end{proof}

@@

In addition to typing judgements, in order to show that a protocol is
secure, we need to classify all corrupt views as shares, all
public values as secure openings, and all outputs as reconstructed
shares by adding them to $\Gamma$. We capture this formally with the following notion of
type environment closure.
\begin{definition}
  \label{def-sty-closed}
  $\Gamma$ is \emph{closed for $\prog$} iff for all $H,C$,
  for all $x \in \houtputs$ there exists $\phi$ such that either
  $([x,\phi] : \sharety) \in \Gamma$ if $C = \setit{1}$
  or  $([\phi,x] : \sharety) \in \Gamma$ if $C = \setit{2}$,
  and for all $\out{\cid} \in O$ we have $(\pubx{\out{\cid}} : \outty) \in \Gamma$.
\end{definition}
Now, the following is a consequence of Definitions \ref{def-OK} and \ref{def-sty-closed}, and then
our main Theorem \ref{theorem-sty} follows by Lemma \ref{lemma-OK} and Theorem \ref{theorem-OK}.
\begin{theorem}
  \label{theorem-OK}
  If $\prog,\Gamma,R : {OK}$ and $\Gamma$ is closed
  for $\prog$, then $\prog$ satisfies noninterference modulo output. 
\end{theorem}
\begin{proof}
  Let $\iov(\prog) = S \cup V \cup O$ and assume some partitioning $H,C$
  with $H = \setit{b}$ and $C = \setit{a}$ for $a,b \in \setit{1,2}$.
  %For any $\out{\cid} \in O$ with $\Gamma,\toeq{\prog} \vdash \pubx{\out{\cid}} : \outty$
  %we can assume wlog that $(\out{\cid} : \outty) \in \Gamma$, since we can
  %add the binding to $\Gamma'$ with  $\prog,\Gamma',R  : {OK}$ by Lemma
  %\ref{lemma-OK}.
  Let $\Phi_a$ and $\Phi^o$ be as defined in Definition \ref{def-OK}. 
  By Definition \ref{def-sty-closed} we have that $x \in \houtputs$
  implies $x \in \Phi_a$ and $(\out{\cid} : \outty) \in \Gamma$ for all
  $\out{\cid} \in O$. 
  Therefore by Definition \ref{def-OK} (and marginalizing away
  extraneous $(\stt : \sty) \in \Gamma$) we have:
  $$
  \condsep{\progd(\prog)}{(S_C \cup \Phi^o \cup O)}{\houtputs}{S_H}
  $$
  By definition of $\TirName{Output}$ it is also the case that for all
  $\out{\cid} \in O$ we have $\toeq{\prog} \models o \eop \phi$ for some
  $\phi \in \Phi^o$. Therefore since we can assume wlog that all revealed
  values are assigned to outputs, we have
  $
  \condsep{\progd(\prog)}{(S_C \cup O)}{\houtputs}{S_H}
  $,
  so by definition we have that for all $\store \in \runs(\prog)$: 
  $$
  \condd{\progd(\prog)}{S_H}{S_C \cup O}(\store) = \condd{\progd(\prog)}{S_H}{S_C \cup \houtputs \cup O}(\store)
  $$
  which is noninterference modulo output by Definition \ref{definition-NIMO}.
\end{proof}
